\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Term Paper 1}
\author{Minh Nguyen}
\date{March 2, 2022}

\begin{document}


\maketitle

\section*{Abstract}
As mobile phones are becoming inevitable, individuals worldwide should not just celebrate the development they introduce into their lives. Individuals have to remain cautious about how they download and use these apps. The main reason is that the apps come with both positive and negative effects. Mobile apps are crucial in supporting almost every aspect of life. For example, they have boosted research and encouraged academic performance among students and professors. Search engines and online journals in the form of apps make it possible for individuals to acquire their desired data to support learning. Also, mobile apps, mostly social-based, continue to influence effective communication between individuals and their loved ones. Individuals can also entertain themselves through mobile apps that allow access to music, movie, and video-related content. Work-related apps have and continue to ensure efficiency in the workplace by allowing employees to work remotely. They organize work and ensure effectiveness in the operations and performance of teams. Apps such as Uber and Bolt have ensured that individuals can easily move from one place to another by ordering a taxi using their mobile phones. Amazon is an example of an e-commerce platform that connects consumers to manufacturers. Despite the benefits, issues such as hacking, phishing, and online bullying are the risks of using mobile apps. Individuals must learn how to separate apps depending on their usefulness to avoid risks and encourage positive development.

\medskip

\section*{The Impact of Mobile Apps in Our Daily Lives}
Technology continues to advance every second. One significant evidence of this advancement includes the creation of smartphones, which have become an inevitable part of our daily lives. Today's significance of mobile phones can be seen by how they have and continue to transform how individuals interact with each other. The development of mobile applications is why there is over-dependence on mobile phones in doing everything that satisfies our needs. The availability of mobile apps has changed how individuals feel and experience computing. Many apps are used for different purposes. Individuals using smartphones can access mobile apps that focus on communication, mobile banking, e-commerce, transport, gaming and entertainment, and work-related services. Such services offer efficiency and great experience among individuals. Despite the above, mobile apps can also be detrimental to individuals. With rising hacking, malware, and phishing cases, individuals may lose their data to unsuspecting hackers. Also, cases such as online bullying can be experienced if individuals are not careful. Therefore, to understand the position of mobile apps in our daily lives, it becomes crucial to assess how societal members relate to their smartphones and how these mobile apps affect their lives. 

\medskip

\section*{Presenting Positive Mobile Apps Implications in our Daily Life}
Currently, the world has evolved to a point where individuals have access to incredible features and opportunities that their mobile phones offer them. Progressive mobile technology, high internet speed, and advanced smartphone communicative interface provide individuals with innovative mobile computing experiences. The above exist as a result of the development of many mobile applications. To understand the impacts of mobile apps in our lives, it will be important to look at them positively and negatively. The positive impacts are presented in the following manner: 

\medskip

\section*{Boosting Research and Academic Performance}
Research is an important factor to consider in any field of development. Academics, business personnel, communication experts, government officials, and students depend on the internet for research. Smartphones come with research apps that are beneficial to individuals. For example, Google Chrome, Microsoft's edge, and Mozilla Firefox provide individuals with extensive research capabilities. These mobile apps allow individuals to search for essentially anything. Search engine apps connect individuals with many websites and platforms to build on knowledge and skill development.
Anyone who needs something can identify it by just typing anything about it. If it were two decades ago, people would take time before finding the meaning of a word because people depended on paperwork, intangible books, and journal articles \cite{Stocchi21}. The above made it almost impossible for individuals to get information related to their desired work. Today, individuals can also scan images and find their information online. For example, the Google Lens allows one to photograph an item, scan it, and provide different suggestions related to the item. With the above process, it becomes easier for individuals to find items online without struggling through manual searches.

\medskip

\section*{Communication through Social Apps}
Communication has become the centerpiece of development among societal members. Today, many social apps have made it possible to communicate easily. The outcome has included how individuals socialize with each other. Social apps include Facebook, Twitter, Instagram, WeChat, WhatsApp, LinkedIn, and Telegram. These apps ensure connectivity regarding how individuals relate and communicate with each other. Social apps introduce both written and oral communication via texts and video-conferencing capabilities. For example, Instagram uses photo-based communication capabilities to ensure that individuals appreciate each other. People post their pictures and short videos, which others comment about and like. 
Facebook and Twitter have remained instrumental in individuals communicating about different issues surrounding their lives. News agencies post news-related information on emergencies such as wars and earthquakes. Individuals can watch this news and comment on them. Facebook has remained significant in creating hashtags that focus on preventing the occurrence of some situations. For example, the hashtag "Stop Ukrainian War" enables the international community to campaign for peace in the region. It also influences individuals to stop President Putin from continuing with the attack against Ukraine.

\medskip

\section*{Entertainment}
An app such as TikTok has changed how individuals interact with each other. Individuals are provided with a platform for ensuring that they make short videos on various interesting activities. Individuals can make lip-syncing to dance videos that are interesting to view. This is one way through which individuals get entertained. Reels is another app that operates similarly to TikTok. The world comprises several apps that provide entertainment. Spotify, Tidal, and SoundCloud are other important applications that ensure individuals enjoy music. The apps have millions of music that individuals can purchase or listen to freely \cite{Tam20}. Individuals can download music and use it for their development. Regarding movies, different apps provide individuals with an opportunity to relax. 
Netflix, Marvel, Disney movies, and Amazon prime allow individuals to download and stream movies. The platforms do not use cables and are easier to download at all times. YouTube is now a basic mobile entertainment and educational app that ensures individuals access millions of music and tutorial-related videos on different developmental areas. Due to this advancement, many individuals use their smartphones to access millions of movie and music-related content across many platforms via android and iOS apps. The focus is to ensure that individuals gain the right content to enjoy themselves through entertainment. 

\medskip

\section*{Work-related Capabilities}

Companies have continued to diversify their operations by completing tasks to become mobile. Mobile apps nowadays ensure that individuals can work remotely using their mobile phones. For example, LAN and Wireless tethering are applications relevant to modern mobile phones. Individuals can use them to establish a mobile network that can allow computers and laptops to connect to the internet. Apps such as Zendesk, Evernote, Workplace, and Skedulo are mobile apps that ensure individuals can organize their tasks in the best way possible. 
The apps are also crucial in ensuring that employees can form teams through them and work remotely on any associated tasks. Today, such apps take over social media capabilities but convert them to a professional angle \cite{Ulas19}. The apps are also used to undertake tasks for a specialist sector. In turn, these apps are used to fulfill the gap between problem-solving outcomes and complex matters. Employees have an opportunity of using their apps to learn and share knowledge related to their professional areas, influencing streamlining outcomes in work-related processes. Organizations also have an opportunity of tracking performance through mobile apps. These apps can promote measuring and assisting organizations to improve services. They create better working environments and ensure that organizations achieve their goals.

\medskip

\section*{Maintenance of better Health Outcomes and Fitness}
Every societal member strives to maintain a healthy background. Therefore, they are always focused on ensuring that they have tips to improve their health and well-being. Health and fitness apps come in handy when providing information regarding how people can live a healthy life. To begin with, Shopwell, Waterlogged, and Food Intolerances are food-related apps that influence individuals to track their progress with mineral intake. Minerals such as magnesium, iron, and proteins are important for the body \cite{Milne20}. Knowing about mineral intake enables individuals to identify their health and well-being to the type of minerals they consume. Also, they can understand what it means to take some types of food and what to avoid for them to experience their life's longevity. 
There are also apps such as Nike Training Club, Sweat, the Apple Fitness Plus, and Peloton accessible via iOS and android platforms. The apps assist individuals in different exercises to lose weight and maintain fitness. The apps show the various exercises that individuals can undertake to maintain a positive health background. Individuals can use them to lose weight and track their exercises. It also identifies progress on maintaining a positive health background and well-being. Wearable devices connected to these apps continue to increase in number. They are connected to health monitoring apps that enable fitness and influence individuals to stay in shape. The reason is that more consumers are becoming health-conscious now, making it possible for them to find possible information in developing their confidence through having the right body shape and weight. 

\medskip

\section*{Transport and Food Delivery Benefits}
Transport is important in our daily lives. Apps such as Bolt and Uber are crucial for ensuring that individuals can move from one place to another. Bolt and Uber continue to be the two largest mobile taxi companies globally despite not owning any vehicle to support their services. Individuals can order these transport systems to support their movement. Individuals can easily visit their professional environments, learning environments, and home. Nevertheless, e-commerce capabilities surrounding these apps make it possible for individuals to order food and drinks at their convenience \cite{gaber21}. Uber Eats and Bolt Foods are examples of e-commerce platforms under the companies to ensure that individuals can connect to restaurants, bars, and other shopping infrastructure. 
There is Glovo, a global food and drink-based app with similar capabilities, apart from the two companies. E-commerce platforms such as Amazon and Alibaba also have apps that are instrumental in connecting consumers to different manufacturers. The situation influences it easier for individuals to experience a better way of ordering their desired products in the market. Individuals can also use apps such as Airbnb and Booking.com to book trips and reserve their accommodation at any given time. The apps bring hotels and private rooms to mobile interfaces, making it convenient for individuals to book and have the best holiday experiences based on their choices. 

\medskip

\section*{Negative Implications of Mobile Apps to our Daily Lives}
Mobile apps, as discussed above, are important to our daily lives. However, one has to understand that they may not be positive at all times. The main reason is that with the rapid evolution of technology, individuals experience setbacks too. In this case, mobile apps are known to have disadvantages that impact our daily lives. These are discussed through the following:

\medskip

\section*{Hacking and Phishing leading to loss of personal Data}
Mobile phishing continues to be a major problem for unsuspecting mobile users despite many people failing to understand its position and influence. Phishing is fraudulent since it involves obtaining sensitive information and data. Individuals can use this to obtain credit card details, usernames, and passwords. Users can download apps that they may think are great to use. In turn, these apps are implanted with bots that go through the phone to acquire this sensitive data \cite{Leguesse20}. Phishing is similar to hacking, only that it appears as an insidious attack. Due to many individuals moving away from laptops and desktops, hackers and phishers understand that the best move is to launch unsuspecting attacks on mobile phones. The situation has influenced mobile Phishing and hacking to increase in the last few years.

\medskip

\section*{Online Bullying}
Social media platforms are used in large numbers. They come in different apps and focus on unique purposes. For example, TikTok is different from Facebook and Twitter. Despite offering communication and entertainment benefits, these apps also comprise negative implications. The situation may see individuals becoming victims of bullying and slandering. Also, social media platforms have active stalkers looking for unsuspecting users who become their victims. The mental health issues surrounding bullying and stalking include stress, anxiety, and suicidal thoughts. Bullies share sensitive information about their victims, leading to their mental breakdown. 

\medskip

\section*{Conclusion}
The discussion has provided important information regarding the position and impact of mobile apps in our daily lives. It has ensured that anyone with a mobile phone understands the crucial role of these apps in improving lives. The positive implications include mobile apps encouraging research and academic performance efficiency by allowing stakeholders to acquire the correct data. Mobile apps have ensured they provide users with important features such as communication and entertainment, influencing them to enjoy every bit of using these apps. Also, the discussion has focused on the relationship between apps and work. Work-related apps organize tasks and distribute them across teams that work remotely, influencing efficiency in the performance of an organization. Health and fitness-related apps monitor progress in the implications of diet and exercises. E-commerce capabilities also allow individuals to order food and other items online. The reason is due to delivery apps focusing on ensuring individuals acquire their desired products at their comfort. However, issues such as hacking, Phishing, and online bullying are some of the dangers of mobile apps. Despite individuals experiencing positive implications of mobile apps, they have to be careful about using them to avoid negative impacts. 







\end{document}
