\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{March 15, 2022}

\begin{document}


\maketitle

\section*{Summary}
There are multiple coding languages and frameworks to choose from when developing a mobile apps such as React Native and Flutter. Flutter is a portable UI toolkit for building natively-compiled apps across mobile, web, and desktop* from a single codebase \cite{Bartosz21}. React Native is a framework for building native applications using React \cite{Bartosz21}. When comparing React to Flutter, React will come in mind that this is more stable since React first released was in 2015 and Flutter was first released in 2018. But Flutter has been growing rapidly thanks to its beautiful and rich widgets and they have such a strong documentation for whoever want to start Flutter. Moreover, they are more flexible and more performance than React. On the other hand, React already have a strong community base since it's released longer than Flutter, there are also multiple tutorials for whoever want to start as well. Both React Native and Flutter code can easily be used on different type of platforms such as mobile, web, and desktop app developement.

\medskip

Which one is better? In my opinion, there is nothing called the "best" framework/coding languages. Every framework and coding languages have its own strength and specific use cases. So we can choose which one works best on the solution that we need. We can choose to use Flutter if "The app will exert a heavy load on CPU/GPU, The UI will need a lot of detailed customization, There’s a chance the app will go beyond mobile, or the next app will benefit from the experience of the current team, Fit for development on wearable and embedded devices, PCs, and vehicle infotainment systems, Google Ads, Stadia, and Grab use Flutter" \cite{Serhii22}. On the other hand, we can choose React Native if "The app will use the visual representations of UI native components exclusively, The development team of your choice is fluent in JS/React/React Native (which is more likely than Dart fluency), The app is relatively simplistic and meant to be lightweight, The app is web-based and / or mobile (iOS & Android) only, Facebook services, Walmart, and Wix use React Native" \cite{Serhii22}. Overall, there is nothing called perfect, so we need to choose which one will benefit us in a particular project and needs based on the details of Flutter and React that mentioned above.


\printbibliography

\end{document}
