\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{April 13, 2022}

\begin{document}


\maketitle

\section*{Summary}
Since mobile apps has been growing rapidly, there are also mobile apps developers increasing rapidly as well to match the demand of the customers. Many people want to start to build a mobile app. This will be a guide which will explain step by step on how to build an app. First off, we would want to think the app ideas, if you do not have any ideas then think about "What you really need are problems, and they’re everywhere!" \cite{Rahul19}. Basically, it means that think about the problems that you see around you, how would you want to approach and fix that problem. After having an idea on which app to build, step 2 would be identify the need. It is basically means that create a demand in the app which will seek more users to use the app since there is demand, by doing that you can "validate your idea by using the Google Keyword Planner tool to look for the number of people seeking out what you’re trying to do" \cite{Rahul19}. Step 3 would be lay out all the features that you want to put into the app and eliminate all the non-important features. After that, step 4 will be spending some time to design the layout, you want to put some time on this since this will be the first step that will catch user's eyes if you have good design. Then you and your team can start to code. You might want to integrate analytics which will track the amount of downloads and users engagements.

\medskip

After successfully built your app, you might want to look into advertisements. Advertise your app will catch more users into using your app. First, "Build a landing page for your app and build a pre-launch email list" \cite{Chris21}. Basically, having a landing page is necessary since this is where the users can learn more about your app. The second most important thing will be documenting your journey while building the app. Most, if not all app developers journal their progress from the beginning until the end, a road map for any features that you want to put out in the future would be great as well. If you have some kind of money to spend, look into paid marketing. Paid marketing is a vague term but if you are using this method, it will get more users to use your app. Otherwise, you can spread the words through any social media apps about your built app \cite{Chris21}.




\printbibliography

\end{document}
