\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{February 23, 2022}

\begin{document}


\maketitle

\section*{Summary}
The Metaverse has been blowing up after Facebook announced that they will migrate into Metaverse in the future. What is Metaverse? "It's a combination of multiple elements of technology, including virtual reality, augmented reality and video where users "live" within a digital universe. Supporters of the metaverse envision its users working, playing and staying connected with friends through everything from concerts and conferences to virtual trips around to the world" \cite{mike2022}. Basically, it's a VR (Virtual Reality), users can connect with their real life friends and family in the digital universe, they can talk, play, or do anything that they want to do, everything. Not only Facebook will migrate into the VR world so called Metaverse, but also Roblox, Minecraft, Microsoft, etc will looking into migrating into the virtual reality world in the future as well.

\medskip

Trying the virtual reality world can be difficult to comprehend at first, but when you get used to be, it can fools your brain to think that this is the reality world. "A few years ago, while doing research for a virtual reality (VR) program at MIT that I would be running, I donned a VR headset and played a ping-pong game. The game was so realistic that it momentarily fooled my brain. When it ended, I instinctively tried to put the paddle down on the “table” and lean against it.  Of course, the table didn’t exist, and I almost fell over. It was so easy to trick my senses into thinking that virtual world was real that I began to think about what would happen to humanity if we kept developing this technology" \cite{rizwan2022}. This tells us that the virtual reality is so real that they couldn't imagine they are in the virtual reality world, it just seem so realistic. If the world is continuing to develop and change, the virtual reality world could possibly replaced our real life, we could be living in the virtual reality world.

\printbibliography

\end{document}
