\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{March 2, 2022}

\begin{document}


\maketitle

\section*{Summary}
There are multiple ways to increase users engagement to any mobile apps such as Prioritize Performance and Usability, Encourage Signups on Other Marketing Channels, Build an Intuitive Onboarding Program, Incentivize with Rewards, Offer In-App Customer Support \cite{syed21}. Those are the five methods that can boost mobile apps engagement. Since mobile apps has blown up in this century, mobile dev should be looking for any possible ways that they can in order to increase users engagement to the app so that the app can have more revenue so that it can grow and expand more bigger.

\medskip

In order to make users engagement, first the mobile app dev should be looking deep into how to make the app attract to the users \cite{helen21}, then it will have users engagement. "The social factor implies the participation in the campaign of iconic figures who the target audience respect and even worship. In this case, we’re talking about virality, i.e. the viral distribution of the information. And distributors are the users themselves. The viral effect could be appreciated much higher, and it can work more efficient than any other PR tools when using the right approach" \cite{helen21}. To make the app to be known, it should be advertised through social and content factors. After that the mobile app dev can focusing on how to make engagement using the five methods, Prioritize Performance and Usability, Encourage Signups on Other Marketing Channels, Build an Intuitive Onboarding Program, Incentivize with Rewards, Offer In-App Customer Support so that they can make their app more popular.

\printbibliography

\end{document}
