\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{April 20, 2022}

\begin{document}


\maketitle

\section*{Summary}
When it comes to coding, you probably heard about Github. Github is a repository hosting service. Github is important and necessary when it comes to any software engineer and/or anything related coding out there. By using Github, you will have multiple benefits to make your repository much more professional. For open-source project, it is so easy to contribute to it, just fork a project and pull the request after making changes to the project. Github also help users to make excellent and professional documentation by provided guides and help articles \cite{Ekaterina18}. Moreover, when a team working on the same project and each person doing their own work and submit it on Github, it will show and track all the revisions that were changed including who changed what, and when, and which files. \cite{Ekaterina18}

\medskip

Even though Github is the most popular one among other competitors, it has some pros and cons and some people will consider Github alternative as well. There are many Github alternatives out there such as GitLab, Gitolite, Gitea, etc \cite{Tom21}. These also have their pros and cons as well. But to be honest, Github is the most popular one and people have been using it for years, it makes their coding lifestyle much more easier. Their competitors will have a hard time competing with Github because of how popular Github has been. If people find it difficult to use Github and/or they don't like Github, they can explore any alternatives out there. \cite{Tom21}




\printbibliography

\end{document}
