\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{February 9, 2022}

\begin{document}


\maketitle

\section*{Summary}
Since mobile apps has been blown up in the past decades, the mobile games industry are blown up as well. "The mobile gaming market generated a combined 7.4 billion dollars from player spending across both app stores in January 2022, which represents a slight dip of 7 percent compared to 2021" \cite{anne2022}. People nowadays are spending so many money into mobile gaming apps such as PUBG mobile, Genshin Impact, etc. Before mobile apps blown up, people mostly spending their time playing video games on PC, consoles, etc anything beside mobile. Now, people has been migrating to mobile for gaming, it is not that PC and consoles gaming are dying, people just do not want to sit on their PC and TV all day to play video games. Mobile gaming is much easier and not time consuming, since you can play anywhere anytime. By looking at the revenue, we can see that mobile gaming has been blown up around the world.

\medskip

Not only mobile gaming industry has been blown up, but also social media apps such as Tiktok, Youtube, Tinder, etc has been blown up as well especially Tiktok. "First-time installs remain relatively flat when compared to 2020, growing 0.5 percent Y/Y across the App Store and Google Play to 143.6 billion in 2021 from 142.9 billion in 2020. This is driven mainly by app adoption on Google Play, which will see installs climb 2.6 percent Y/Y to 111.3 billion from 108.5 billion; Apple's marketplace will generate about 32.3 billion installs this year, down 6.1 percent from 34.4 billion" \cite{stephanie2021}. This states that the users that install the app for the first time did not change much compared to 2020. Tiktok has been dominating in the China marketplace "surpassed 3 billion dollars in lifetime revenue earlier this year—in the first 11 months of 2021, the app saw 2 billion dollars in revenue, up 67 percent Y/Y from 1.2 billion dollars" \cite{stephanie2021}. This shows us that not only mobile gaming dominating the mobile apps industry, but also social media apps (non-gaming) are dominating the mobile industry as well.

\printbibliography

\end{document}
