\documentclass{article}
\usepackage[natbib]{biblatex}
\usepackage{indentfirst}



\addbibresource{bibliography.bib}

\title{Bibliography Summary}
\author{Minh Nguyen}
\date{April 6, 2022}

\begin{document}


\maketitle

\section*{Summary}
There are many apps that we can watch to get entertained from such as Youtube and Tiktok. Youtube has been the most popular video app since around 2005, we can watch any type of videos on Youtube such as tutorials, musics, etc. Tiktok has been around for about 2 years since it first started in the US in 2020. "The benefit of YouTube having more experience as a platform is how its features have matured. For example, you can see an entire library of videos you've liked in the past. You can create multiple playlists that contain your favorite videos based on different topics. You also have access to your entire history of watched videos, or you can add videos to a playlist to watch later." \cite{Raul21}. Youtube have a bigger advantage compared to Tiktok in term of managing watched videos history, Tiktok has the ability to see liked video history but doesn't have watched videos history. Moreover, Tiktok doesn't have the ability to create a playlist of watched video history. This advantage put Youtube better than Tiktok in term of managing contents. As a result, "YouTube has a lot more experience and it shows. You're able to search through a large catalog of high-quality videos to find all types of content with any length you want. You can store the videos for watching at a later time and organize them with playlists too." \cite{Raul21}. But we can't deny that Tiktok is a greate platform which got so popular in the last 2 years, it is a great platform for entertainment.

\medskip

Which platform is great for content creators someone would ask? Tiktok content creators only allowed to post video with length about 3 minutes, on the other hand, Youtube content creators should make a video with a length more than 10 minutes in order to get money from views. When it comes to affiliate marketing and ads, both platforms are pretty alike, "creators can generate revenue by adding affiliate links for products or services in uploaded content and sponsored videos." \cite{Christie21}. Both platforms pay their content creators to post tutorials, reviews, unboxing videos, etc. "YouTube universe is forever changing and expanding, with content becoming more educational, funnier, professional, and informative. TikTok can’t compete with YouTube, as they share entirely different videos." \cite{Christie21}. Youtube has been around for so long that they keep developing and futuristic their app, they expand into educational and professional contents, it is really hard for Tiktok to catch Youtube in this case. But both platforms are great for content creators, Youtube has different variety of categories that content creators can choose from.




\printbibliography

\end{document}
